---
title: "Assignment 2"
author: "Connor Schnable"
date: '2022-04-07'
output:
  html_document: default
  pdf_document: default
---
This dataset is one that captures the power rankings of 86 different candies. Some of the variables include: "chocolate, fruity, peanutyalmondy, nougat, crispedwafer, hard, bar, pluribus, sugarpercent, pricepercent, winpercent." This was collected by asking over 8,000 people about 269,000 randomly generated matchups between candies. I am hoping to answer a simple question, "Which candy is the best candy based on these results?" The data is saved in a chart on a csv file. A csv file is a flat file and is delimited since each character is separated by a comma. The program that most commonly opens a csv is microsoft word. But there are tons of software examples that can open up a csv. 
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
candy_data <- read.csv("candy-data.csv")
#I used the simple read.csv to read in the csv file with the data in it. 
library(dplyr)
```


```{r}
select(candy_data,chocolate,winpercent)
summarise(candy_data,winpercent)
chocolate<-filter(candy_data,chocolate==1)
Highwin<-filter(candy_data,winpercent>=50)
```
#This dataframe has `r nrow(candy_data)` rows and `r ncol(candy_data)` columns


```{r}
text_tbl<-data.frame(chocolate)
Names=c("chocolate","winpercent")
Description=c("1 if the candy is chocolate,0 if not","Shows the percentage at which that candy won its matchup")
text_tbl
```


```{r}
#Picking three columns to use summary function 
data_pick3<-select(candy_data,chocolate,sugarpercent,pricepercent)
```
```{r,include=TRUE}
summarytable<-summary(data_pick3,candy_data)
summarytable
```



